perhaps rotations are better than sequences ?

### 2018-03-22 inst/documents/phaps-rotations-better.Rmd
finding when rotations and sequences favoured

@@

resistance frequencies seem to take longer to rise for rotations than sequences once cost (or rufugia) are included. 
particularly when the rotation interval is short

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=9}

@@

ggrot <- rot_plot_resistance(dfrot, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
ggseq <- rot_plot_resistance(dfseq, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
library(gridExtra)
grid.arrange(ggrot, ggseq, ncol=1)
gens_under_thresh(dfrot)
gens_under_thresh(dfseq)

@@

>>>>

```{r, eval=TRUE, include=FALSE}

library(knitr)
#https://stackoverflow.com/a/36234023/1718356 for fig.pos = 'h'

opts_chunk$set(fig.height=7, fig.width=9, fig.pos = 'h', echo=FALSE, warning=FALSE, message=FALSE)

@@

Resistance frequencies can take longer to rise for rotations than sequences once cost (or refugia) are included. 
Particularly noticeable when the rotation interval is short, costs (0.1) and dominance (1) high.

Can this be a simple mathematical result of:

1. slower rate of resistance frequency change at lower resistance frequencies. 
2. rotation initially keeps frequencies lower where this rate of change is less.

```{r, eval=TRUE}

@@

ggrot <- rot_plot_resistance(dfrot, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
ggseq <- rot_plot_resistance(dfseq, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
library(gridExtra)
grid.arrange(ggrot, ggseq, ncol=1)
grot <- as.numeric(gens_under_thresh(dfrot))
gseq <- as.numeric(gens_under_thresh(dfseq))
cat('sum generations deployed insecticide under threshold rotation:', grot,' sequence:',gseq)

print(unlist(linputs))

@@

\pagebreak

Cost reduced from 0.1 to 0.02. Radically cuts difference between rotation and sequence.

```{r, eval=TRUE}

linputs$n_insecticides <- 2
linputs$coverage <- 1
#linputs$migration <- 0.1
linputs$cost <-     0.02 
linputs$max_gen <-  200
linputs$expo_hi <-  0.6
linputs$eff <-      0.6
linputs$dom_sel <-  1
linputs$dom_cos <-  1
linputs$plot <-     FALSE

ggrot <- rot_plot_resistance(dfrot, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
ggseq <- rot_plot_resistance(dfseq, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
library(gridExtra)
grid.arrange(ggrot, ggseq, ncol=1)
grot <- as.numeric(gens_under_thresh(dfrot))
gseq <- as.numeric(gens_under_thresh(dfseq))
cat('sum generations deployed insecticide under threshold rotation:', grot,' sequence:',gseq)

print(unlist(linputs))

\pagebreak

Decreasing dominance of resistance and cost from 1 to 0 (had to increase exposure, effectiveness and rr to get similar times-to-resistance). Then the difference between rotation and sequence is less.

```{r, eval=TRUE}

linputs$n_insecticides <- 2
linputs$coverage <- 1
#linputs$migration <- 0.1
linputs$cost <-     0.02 
linputs$max_gen <-  200
linputs$expo_hi <-  0.8
linputs$eff <-      0.8
linputs$rr  <-      0.8
linputs$dom_sel <-  0
linputs$dom_cos <-  0
linputs$plot <-     FALSE

ggrot <- rot_plot_resistance(dfrot, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
ggseq <- rot_plot_resistance(dfseq, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
library(gridExtra)
grid.arrange(ggrot, ggseq, ncol=1)
grot <- as.numeric(gens_under_thresh(dfrot))
gseq <- as.numeric(gens_under_thresh(dfseq))
cat('sum generations deployed insecticide under threshold rotation:', grot,' sequence:',gseq)

print(unlist(linputs))

\pagebreak

Dominance of cost 0 and dom_sel 1.

Benefit of rotation is lost, sequence lasts a tiny bit longer. Suggests it is a high dominance of cost that favours sequence over rotation.

```{r, eval=TRUE}

linputs$n_insecticides <- 2
linputs$coverage <- 1
#linputs$migration <- 0.1
linputs$cost <-     0.1 
linputs$max_gen <-  200
linputs$expo_hi <-  0.6
linputs$eff <-      0.6
linputs$dom_sel <-  1
linputs$dom_cos <-  0
linputs$plot <-     FALSE

ggrot <- rot_plot_resistance(dfrot, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
ggseq <- rot_plot_resistance(dfseq, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
library(gridExtra)
grid.arrange(ggrot, ggseq, ncol=1)
grot <- as.numeric(gens_under_thresh(dfrot))
gseq <- as.numeric(gens_under_thresh(dfseq))
cat('sum generations deployed insecticide under threshold rotation:', grot,' sequence:',gseq)

print(unlist(linputs))

\pagebreak
dom_sel and dom_cost 0.1, small favour of rotation

```{r, eval=TRUE}

linputs$n_insecticides <- 2
linputs$coverage <- 1
#linputs$migration <- 0.1
linputs$cost <-     0.1 
linputs$max_gen <-  200
linputs$expo_hi <-  0.8
linputs$eff <-      0.8
linputs$dom_sel <-  0.1
linputs$dom_cos <-  0.1
linputs$plot <-     FALSE

ggrot <- rot_plot_resistance(dfrot, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
ggseq <- rot_plot_resistance(dfseq, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
library(gridExtra)
grid.arrange(ggrot, ggseq, ncol=1)
grot <- as.numeric(gens_under_thresh(dfrot))
gseq <- as.numeric(gens_under_thresh(dfseq))
cat('sum generations deployed insecticide under threshold rotation:', grot,' sequence:',gseq)

print(unlist(linputs))

### 2018-03-22 inst/documents/rotations_notes.Rmd
finding when rotations and sequences favoured

@@

@@

~ compare dfrot & dfseq for above example

>>>>

What value of cost did Rowland1991 use ? Seems that he used high costs of 0.46 and 0.35, see table 8.

@@

eek
      0 [main] us 0 init_cheap: VirtualAlloc pointer is null, Win32 error 487
AllocationBase 0x0, BaseAddress 0x68570000, RegionSize 0xE0000, State 0x10000
C:\Program Files (x86)\Git\bin\ssh.exe: *** Couldn't reserve space for cygwin's heap, Win32 error 0
fatal: Could not read from remote repository.

Please make sure you have the correct access rights
and the repository exists.

@@

~ look more at phaps-rotations-better.Rmd
